Conference Paper Title\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-03-11 paper/paper.tex
added more figures, paragraphs

>>>>

To see the distribution of the demographic of the papers in terms of age, 
we look at the number of papers in our updated WoS database, as in Figure 2 
below. From this graph, we see that papers have been released more frequently 
in recent years. This implies that machine learning hardware is a rising field, 
which follows given the recent popularity of machine learning as a field in general. \par

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.3] {papers_by_year.png}}
    \caption{Growth of Papers Published in ML Hardware over Time.}
    \label{fig}
\end{figure}

After applying these changes, we define a t-SNE visualization on the dataset, 
as pictured in Figure 3. The plot helps to establish underlying patterns and 
relationships in the dataset on a 2-D plane for reader understandability. 
From this plot, we see that there are some strong clusters of papers and 
some much weaker, though still characteristic. \par

Then, after finding the edge list of the dataset, we can plot the degree distribution 
chart of the network, plotting the number of times a paper was cited against the 
frequency of that number of citations, shown in Figure 5 below. \par

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.3] {tsne_embeddings.png}}
    \caption{t-SNE Plot of the WoS Dataset.}
    \label{fig}
\end{figure}

From this plot, we establish that the WoS citation network shows 
characteristics of a small-world network, with few nodes exhibiting 
a high number of citations and most having very few citations. 
This result makes sense, as few papers are likely to have a high 
impact, and those that do are likely to influence many papers. \par

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.3] {times_cited.png}}
    \caption{Occurrences for papers with certain times cited.}
    \label{fig}
\end{figure}

Looking at the most-cited nodes, we find impactful key publications 
in their respective fields. One such publication is “Equivalent-accuracy 
accelerated neural-network training using analogue memory”, published in 2016 [7]. 
In “Nanoscale memristor device as synapse in neuromorphic systems'' published 
in 2018,  Jo et al. experimentally show a nanoscale memristor working within 
the context of neuromorphic computing [8]. In another example, “Memory devices 
and applications for in-memory computing” gives an overview of potential solutions 
to in-memory computing, including solutions closely related to machine learning and 
digital signal processing [9]. \par

In finding additional outliers, we were also able to distinguish the age of our papers. 
The dataset consisted of papers from the years of 1971 to 2023. Since machine 
learning was identified as a rising field from the discussion regarding Figure 2, 
there were many papers from 2023. And, since many papers only provided a month as 
the date of publication, the multiple papers from November of 2023 prevented the 
identification of the newest paper. However, the oldest paper, the only paper from 
1971, was titled “Unit Spike Activity in Coelenteran Neural Network”, a paper about 
temperature spikes in primitive neural nerve networks [10]. \par

While both Cora and Citeseer categorize publications and have vocab dictionaries, 
there are no such categories or dictionaries for Web of Science results. 
Therefore, we utilized the search function to specify the categories to be 
both used and excluded in each search. To match the vocabularies of Cora and 
Citeseer, we utilized spacy for trained keyword extraction models, finding 
the top 10 unigrams with the most significance in each abstract, and used 
these words to construct our vocabulary vectors [11].
